Union and intersection contracts are hard, actually

### 2021-06-10 paper.tex
Fix code example

This same property is desirable of contracts as well, otherwise we
lose an important benefit of dynamic checking. Preferably, we want to
be able to extend the universe of contracts with user-defined
predicates.

@@

\resolved{Arnaud: this paragraph is pretty good, on the other hand, there
is no value which lets me complete the example, so this example falls
a bit flat.
Teo: Improved the example, also added another one commented that is, for me,
more realistic, but I think the one uncommented is simpler.}
We have shown how values of a union are built, is worth mentioning
how they are used.
For instance, consider the TypeScript function on Figure \ref{fig:addElem},
we want it to insert an element to a list that is either an
\typescript{Array< 42 | "Nickel" >} or an \typescript{Array< "Nickel" | 3.5 >},
where \typescript{42}, \typescript{3.5}, and \typescript{"Nickel"} are literal
types\footnote{Note that in TypeScript, union and intersection are written as
\typescript{|} and \typescript{&}, instead of \nickel{@|} and \nickel{@&},
as we do in Nickel.}.
What value could we fill the square ($\square$) with for this to typecheck?
Since we don't know what's the shape of \typescript{list},
we can't know whether to push a \typescript{42 | "Nickel"} or a
\typescript{"Nickel" | 3.5}. In general,
when using a union, we have to treat it as if it were any one
of the alternatives. In the case of the example, we should provide
it with a value that could be pushed to both arrays, the only possible one
is \typescript{"Nickel"},
since it's the only value that satisfies the intersection of
\typescript{42 | "Nickel"} and \typescript{"Nickel" | 3.5}.

@@

Yet, intersections are useful in their own right. They can be used to
combine dictionaries in the style of object-oriented inheritance. For instance, in
Figure \ref{fig:intersection-record} two types are defined
\nickel{Animal} and \nickel{Pet}, and a variable that is compatible
with both types is declared, with type \nickel{Animal @& Pet}. This
particular application is supported, for instance, by TypeScript.

>>>>

This same property is desirable of contracts as well, otherwise we
lose an important benefit of dynamic checking. Preferably, we want to
be able to extend the universe of contracts with user-defined
predicates (sometimes called flat contracts).

@@

\resolved{Arnaud: this paragraph is pretty good, on the other hand, there
is no value which lets me complete the example, so this example falls
a bit flat.
Teo: Improved the example, also added another one commented that is, for me,
more realistic, but I think the one uncommented is simpler.}
We have shown how values of a union are built, is worth mentioning
how they are used.
For instance, consider the TypeScript function on Figure \ref{fig:addElem},
we want it to insert an element to a list that is either an
\typescript{Array< 42 | "Nickel" >} or an \typescript{Array< "Nickel" | 3.5 >},
where \typescript{42}, \typescript{3.5}, and \typescript{"Nickel"} are literal types
\footnote{Note that in TypeScript, union and intersection are written as
\typescript{|} and \typescript{&}, instead of \nickel{@|} and \nickel{@&},
as we do in Nickel.}.
What value could we fill the square ($\square$) with for this to typecheck?
Since we don't know what's the shape of \typescript{list},
we can't know whether to push a \typescript{42 | "Nickel"} or a
\typescript{"Nickel" | 3.5}. In general,
when using a union, we have to treat it as if it were any one
of the alternatives. In the case of the example, we should provide
it with a value that could be pushed to both arrays, the only possible one
is \typescript{"Nickel"},
since it's the only value that satisfies the intersection of
\typescript{42 | "Nickel"} and \typescript{"Nickel" | 3.5}.

@@

Yet intersections are useful in their own right. They can be used to
combine dictionaries in the style of object-oriented inheritance. For instance, in
Figure \ref{fig:intersection-record} two types are defined
\nickel{Animal} and \nickel{Pet}, and a variable that is compatible
with both types is declared, with type \nickel{Animal @& Pet}. This
particular application is supported, for instance, by TypeScript.
